A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-02 tex/codatadp.tex
more

  * less briefly: codatatypes and why they are useful
    * in Agda, Coq, Matita -- recently also in Isabelle/HOL \cite{nipkow-et-al-2002}
    * but not in SMT-LIB 2 \cite{xxx}

@@

Function symbols are written in a sans-serif font (e.g., $\const{f}$, $\const{g}$) to
distinguish them from variables (e.g., $x$, $y$). With each function symbol \const{f}
is associated a list of argument types $\tau_1,\ldots,\tau_n$ (with $n \ge 0$)
and a return type $\tau$. This connection can be expressed compactly as
$\const{f} : \tau_1 \times \cdots \times \tau_n \to \tau$
(which collapses to $\const{f} : \tau$ if $n = 0$).
For a term $t$, the notation $t : \tau$ indicates that $t$ has type $\tau$.
Functions are applied the standard way, with $\const{f}(t_1,\ldots,t_n)$
applying the $n$-ary function symbol
\const{f} to $n$ well-typed arguments $t_1 : \tau_1$, \ldots, $t_n :
\tau_n$. Nullary function symbols are called constants and can appear as is in
terms, without parentheses.

>>>>

  * less briefly: codatatypes and why they are useful
    * in Agda, Coq, Matita -- recently also in Isabelle/HOL \cite{nipkow-et-al-2002}
    * but not in SMT-LIB 2 \cite{barrett-et-al-2010}

@@

Function symbols are written in a sans-serif font (e.g., $\const{f}$, $\const{g}$) to
distinguish them from variables (e.g., $x$, $y$). With each function symbol \const{f}
is associated a list of argument types $\tau_1,\ldots,\tau_n$ (with $n \ge 0$)
and a return type $\tau$. This connection can be expressed compactly as
$\const{f} : \tau_1 \times \cdots \times \tau_n \to \tau$
(which collapses to $\const{f} : \tau$ if $n = 0$).
For a term $t$, the notation $t : \tau$ indicates that $t$ has type $\tau$.
Functions are applied the standard way, with $\const{f}(t_1,\ldots,t_n)$
applying the $n$-ary function symbol
\const{f} to $n$ well-typed arguments $t_1 : \tau_1$, \ldots, $t_n :
\tau_n$. Nullary function symbols are called constants and can appear without
parentheses in terms.
